25-Figure3-051821

### 2021-11-18 notebooks/03-Fig3abde_4acd-051821.Rmd
fixed issues running snakemake

```
# Figure3
## A
```{r}
sensor_neighbor_degree_plot <- pcc_df %>%
  mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
  geom_boxplot() +
  theme_bw() +
  ylab("Log(Average neighbor degree)") +
  xlab("") +
  stat_compare_means() +
  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
  sensor_neighbor_degree_plot

@@

>>>>

```
# Figure3
## A
```{r}
#sensor_neighbor_degree_plot <- 
pcc_df %>%
  mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
  group_by(is_sensor)%>%
    summarise(mean = mean(neighbor_degree), median = median(neighbor_degree))

@@

```{r}
25.18/3.38
```

```{r}
20.7/3
```
